---
title: "Data Analysis for the Life Sciences - Getting Started"
output: html_notebook
---

Let's blast through the introduction and getting started segment. I imagine it's a good thing to do these anyway since I often forget what I did last time. 

## Getting Help
```{r}
?install.packages
help("install.packages")
```

## Installing packages
````{r}
install.packages("rafalib")
install.packages("downloader")		#the download.file function
install.packages("devtools")		#To install packages from GitHub
````












## Importing Data into R
The book mentions using CSV files and whatnot. I spent a good deal of time making a postgres database and we're gonna use that. 
````{r}
#The requisite packages are:
install.packages("RPostgreSQL", "RPostgres")
library(DBI)
library(sqldf)
library(RSQLite)

#The setup for variables for a postgres connection look like:
usr <- "ruser"
psw <- {"RassWord!"}
drv <- RPostgres::Postgres()
hst <- "localhost"
prt <- 5432
dbn <- "project10"	

#Connecting/establishing a connection to the DB looks like
project12 <- dbConnect(drv, dbname = dbn, host = hst, port = prt, user = usr, password = psw)

#issuing a db SQL querry looks like:
numberofrowsQuery <- dbGetQuery(project12, "SELECT COUNT(VAERS_ID) from vaers;")

#some built in commands
dbListTables(project12) 
````









## Download data from within R
The book stores many of the datasets used on GitHub20. Using the download.file function in the downloader package to download the file to a specific location and then read it in. 

TODO, imagine turning this into a function to download data files and then churn them into the DB? How cool would that be.

````{r}
library(downloader) ##use install.packages to install
url <- "https://raw.githubusercontent.com/genomicsclass/dagdata/master/inst/extd\ata/femaleMiceWeights.csv"
filename <- "femaleMiceWeights.csv"
download(url, destfile=filename)

#We can then read it in like this:
dat <- read.csv(filename)
 
````








Install a package from GitHub. 
````{r}
install.packages("devtools")		#To install packages from GitHub
install_github("genomicsclass/dagdata")
library(devtools)

# Once you install the package, the file is on your computer. However, finding it requires advanced knowledge:

dir <- system.file(package="dagdata") #extracts the location of a package
list.files(dir)

list.files(file.path(dir,"extdata")) #list files in a directory

#read in the file
filename <- file.path(dir,"extdata/femaleMiceWeights.csv")
dat <- read.csv(filename) 
````













## Notes 
Are there any worthy notes or anything we want to keep around?
````{r}

````